---
title: "Assessment 1"
author: "Prateeksha 4658793"
date: "28/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(skimr)
library(mapproj)


```
# **R Markdown is a file format for making dynamic documents with R.** An *R Markdown document is written in markdown* (an easy-to-write plain text format) and contains chunks of embedded R code#


```{r fastfood}

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv") #assigning variable fastfood

```


```{r 1}

fastfood10 <- fastfood %>% head(10) #displaying first 10 rows of fastfood. 


knitr::kable(fastfood [1:10, 1:5]) #displaying first 10 rows and 5 variables

fastfood10 %>% filter( calories>1000) #displaying calories more than 1000

dont_eat_this <- fastfood10 %>% filter(total_fat>40 & total_carb>80) #displaying the observations with total fat > 40 and total_card>80 and assigned to variable dont_eat_this

```


```{r}

Mcdonalds <-  fastfood %>% filter(restaurant == "Mcdonalds") #displaying restaurant Mcdonalds

```




```{r skimr}

Variables <- skim(fastfood) %>%
  dplyr::select(skim_variable)  # displaying types of variables using skim
```


```{r counting}
fastfood %>%
  count(restaurant, sort = TRUE) %>%
  kable()  #counting observations of each restaurant
```


```{r grouping}
averagecalories <- fastfood %>%
  group_by(restaurant) %>%
  summarise(mean(calories))  #displaying average no of calories per type of restaurant

```


```{r mutating}
addingcalories <- fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories = mean(calories)) %>%
  ungroup() # adding new variable average_calories to the existing data set
```


```{r fat}
addingcalories %>% 
  group_by(restaurant) %>% 
  summarise(max(total_fat)) %>%
  ungroup()                                           #displaying total fat per each type of restaurant

```


```{r mutating fat}
final <- addingcalories %>%
  group_by(restaurant) %>%
  mutate(max_total_fat = max(total_fat)) %>%  
  ungroup()   #adding Max_total_fat to existing data set
```


```{r ggplot}

ggplot(final, aes(restaurant, max_total_fat, fill = restaurant)) +
  geom_col() #displaying total fat per restaurant.

```


#ggplot2 is a plotting package that makes it simple to create complex plots from data in a data frame. It provides a more programmatic interface for specifying what variables to plot, how they are displayed, and general visual properties.#




```{r plotting}

final %>% filter(restaurant == "Mcdonalds") %>% ggplot(aes(x=sugar,y=protein, colour = restaurant, size = sugar)) +
  geom_point()

#displaying protein and sugar 


```


```{r factor}
class(final$restaurant)  #identifying variables that can be converted as factors

final2 <- as_factor(final$restaurant) #converting the variable data type


calories_type <- cut_number(final$calories, n = 3, labels=c("low", "med", "high")) 
 levels(calories_type)    #making groups using cut_number functions

fastfood <- final %>% mutate(fct_relevel(calories_type)) #adding the variable to data type

```




```{r plotting again}

fastfood %>% ggplot(aes(calories_type,restaurant,)) +
  geom_col() +
   coord_flip() +
  facet_wrap(~restaurant) +
  theme_linedraw()

```




```{r adding}

fastfood <- fastfood %>% mutate(trans_fat_percent = trans_fat/total_fat * 100)

#show the percentage of `trans_fat` in `total_fat`

```








```{r plots}
 
  ggplot(fastfood, aes(trans_fat_percent,restaurant,fill = restaurant)) + 
  geom_col() +
   coord_flip() +
  theme_linedraw()

```


```{r totalfat}

totalfat <- fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat = mean(total_fat)) #show the average (mean)  `total_fat` for each type of restaurant
  

```


```{r totalfat plot}

 ggplot(totalfat, aes(total_fat, restaurant, fill = restaurant)) +
  geom_col()

```
